\textls[-0]{\thetitle}

### 2023-03-23 metatheory-condensed.tex
fix margin overrun

Derived families can be modeled as linkage transformers inductively
constructed from the introduction forms
$\small\InhId$, $\small\InhExt{h}{\mathit{self}.t}$, $\small\InhOv{h}{\mathit{self}.t}$, %$\small\InhInh{h}$,
etc.
\cref{fig:fmltt-selected} shows the $\beta$-rule of an exemplary transformer,
\ruleref{tmeq/ov/beta}.
It states that applying the transformer $\small\InhOv{h}{\mathit{self}_{\!2}.t_2}$ to
a linkage of form $\LkgAdd{\lkg}{\mathit{self}_{\!1}.t_1}$
overrides the linkage's last field~$t_1$ with~$t_2$.
For instance, the construction below shows that 
$\small\InhOv{\InhId}{\mathit{self}.\wcode{\wsig'_{\texttt{tm}}}}$
is used as the first step in creating a linkage transformer modeling a derived family that
overrides $\wsig_{\texttt{tm}}$ with an extended
signature~$\wsig'_{\texttt{tm}}$:
\vspace{.9ex}

>>>>

Derived families can be modeled as linkage transformers inductively
constructed from the introduction forms
$\small\InhId$, $\small\InhExt{h}{\mathit{self}.t}$, $\small\InhOv{h}{\mathit{self}.t}$, %$\small\InhInh{h}$,
etc.
\cref{fig:fmltt-selected} shows the $\beta$-rule of an exemplary transformer,
\ruleref{tmeq/ov/beta}.
It states that applying the transformer $\small\InhOv{h}{\mathit{self}_{\!2}.t_2}$ to
a linkage of form $\LkgAdd{\lkg}{\mathit{self}_{\!1}.t_1}$
overrides the linkage's last field~$t_1$ with~$t_2$.
For instance, the construction below shows that 
$\small\InhOv{\InhId}{\mathit{self}'\!.\wcode{\wsig'_{\texttt{tm}}}}$
is used as the first step in creating a linkage transformer modeling a derived family that
overrides $\wsig_{\texttt{tm}}$ with an extended
signature~$\wsig'_{\texttt{tm}}$:
\vspace{.9ex}
